Title

### 2024-05-07 paper/main.tex
Updates

\begin{abstract}
	Causal discovery is a fundamental problem in causal inference, and
	numerous algorithms have been developed to address it. However, their
	adoption in applied disciplines  has been limited, possibly due to a
	lack of confidence in these algorithms stemming from them making
	obvious mistakes, and the difficulties in choosing the right algorithm
	for specific datasets. Consequently, in applied disciplines, these
	causal Directed Acyclic Graphs (DAGs) are predominantly constructed
	manually based on domain expertise. This makes it vital to test and
	potentially modify these models against data before using them for any
	analysis. Local testing based on Conditional Independence tests and
	their effect sizes have been commonly used for this purpose. However,
	one of the current limitations of this approach is that there are no
	effect sizes for mixed data. To address this, we introduce a novel
	effect size measure for mixed data based on canonical correlations.
	This effect size is a generalization of some of the effect sizes used
	in special cases to mixed variables. Moreover, to assist researchers in
	constructing DAGs manually, we use the proposed mixed data effect size
	measure to build a web-based tool that can help researchers in
	constructing, validating, and modifying their DAGs with the help of
	available data. The tool iteratively suggests modifications to DAGs
	based on correlations that are not explained/over-explained by the DAG,
	while the expert chooses the direction of the edge between those
	variables. Empirically, we show that taking a greedy approach on the
	tool's recommendations can perform comparably to causal discovery
	algorithms, provided that the expert correctly determines the direction
	of the edges in at least one out of three cases, with performance
	improving as accuracy increases.
\end{abstract}

@@

\begin{enumerate}
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}

@@

\subsection{Canonical Correlations}
Canonical correlations are generalization of correlations to set of variables.

\section{Effect size for mixed data}
\subsection{Non-conditional Case}
\subsection{Conditional Case}
\subsection{Connection to special cases}

>>>>

\begin{abstract}
	Constructing a Directed Acyclic Graph (DAG) from observational data,
	called causal discovery, is a fundamental problem in causal inference.
	Numerous algorithms have been developed to address it. However, their
	adoption in applied disciplines has been limited, possibly due to a
	lack of confidence in these algorithms stemming from them making
	obvious mistakes, and the difficulties in choosing the right algorithm
	for specific datasets. Consequently, in applied disciplines, these
	causal Directed Acyclic Graphs (DAGs) are predominantly constructed
	manually based on domain expertise. This makes it vital to test and
	potentially modify these models against data before using them for any
	analysis. Local testing based on Conditional Independence (CI) tests and
	effect sizes have been commonly used for this purpose. However,
	one of the current limitations of this approach is that there are no
	effect sizes for mixed data. To address this, we introduce a novel
	effect size measure for mixed data based on canonical correlations.
	This effect size is a generalization of some of the effect sizes used
	in special cases to mixed variables. Moreover, to assist researchers in
	constructing DAGs manually, we use the proposed mixed data effect size
	measure to build a web-based tool that can help researchers in
	constructing, validating, and modifying their DAGs with the help of
	available data. The tool iteratively suggests modifications to DAGs
	based on correlations that are not explained/over-explained by the DAG,
	while the expert chooses the direction of the edge between those
	variables. Empirically, we show that taking a greedy approach on the
	tool's recommendations can perform comparably to causal discovery
	algorithms, provided that the expert correctly determines the direction
	of the edges in at least one out of three cases, with performance
	improving as accuracy increases.
\end{abstract}

@@

\begin{enumerate}
	\item Algorithsm can be biased towards sparse graphs. Ref: Malinsky's paper.
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}

@@

\subsection{Canonical Correlations}
Canonical correlations are generalization of correlations to multi-dimensional case.

Multiple effect sizes measures based on canonical correations are available.

\section{Effect size for mixed data}
In this section, we use canonical correlations to define an effect size for mixed data CI tests. The main idea is to transform any CI test into j
We consider the following two cases separately:

\subsection{No conditional variables}
When we have no conditonal variables, we are trying

\subsection{Conditional Case}

\subsection{Connection to special cases}
